Social Network Activation: \\The Application in Smartphone Use

### 2025-02-04 ProjectBlog/paper2/Paper 2 Slides/P2 Slides.qmd
is studies on network

##
### Study/Methodology
-   We leverage data sets collected from a series of longitudinal studies that tracked participants’ smartphone use, social networks, and physical activities. We measure social network activation in real-time and track its evolution for each participant, combining self-reported social network structure information and real-time mobile communications.

Social isolation ➟ Smartphone Addiction

>>>>

-   We leverage data sets collected from a series of longitudinal studies that tracked participants’ smartphone use, social networks, and physical activities. We measure social network activation in real-time and track its evolution for each participant, combining self-reported social network structure information and real-time mobile communications.
-   Related studies:

<iframe src="pdfs/Yan et al. - 2015 - Network Dynamics How Can We Find Patients Like Us.pdf" style="width:100%; height:1500px;" frameborder="0">

</iframe>
